---
title: "Laptop choice as a Typst PDF vignette"
format:
  typst:
    toc: false
    papersize: a4
    margin:
      x: 1.5cm
      y: 1.5cm
    fontsize: 10pt
vignette: >
  %\VignetteIndexEntry{Laptop choice as a Typst PDF vignette}
  %\VignetteEngine{quarto::format}
  %\VignetteEncoding{UTF-8}
---

## The model, evaluated live

```{r}
library(ahp)
ahpFile <- system.file("extdata", "laptop.ahp", package = "ahp")
laptopAhp <- Load(ahpFile)
Calculate(laptopAhp)
Analyze(laptopAhp)
```

The Chromebook wins with a total weight of 44.7%, driven by Price
(54.0% of the decision). The winning priorities per criterion are
$34.7\%$ (Price), $12.0\%$ (Battery, MacBook) and $10.6\%$
(Ecosystem, MacBook).

## The colored table, natively in Typst

`AnalyzeTable()` returns a `formattable` object, i.e. an HTML table, which
Typst cannot render. `AnalyzeTinytable()` produces the same colored table
as a `tinytable` object, rendered natively in each output format
(HTML, LaTeX/PDF and Typst) — no screenshots needed:

```{r}
AnalyzeTinytable(laptopAhp)
```

For wide tables that do not fit on a Typst page, shrink the font, e.g.
`AnalyzeTinytable(carAhp, fontsize = 0.8)`. The only difference with
`AnalyzeTable()` is that no warning icon is shown for high
inconsistency (the background color is kept).

The screenshot approach (capture the `formattable` table to PNG with
`webshot2` and embed the image) remains available and is documented in
the "Choosing a laptop with AHP" vignette.
